Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2024-06-09 paper/1_Initial/manuscript.qmd
Update manuscript.qmd

![Figure 1. Different ways in which interoception can be measured.](figures/measuring_interoception.png)
<!-- TODO: replace with include_ _figure that allows for legend -->

@@

<!-- Convergent validity (correlates)  -->
Several measures have been used to assess convergent validity for the the IAS, including alexithymia, or neuroticism, or other interoception scales, such as the MAIA, which have previously correlated and used to validate each other [@brand2023]. Recent findings by @campos2021 suggest a significant positive correlation between the BPQ Body Awareness (BPQ-BA) and the IAS, which contradict @murphy2019 findings of the 2x2 factorial model of interoception, in which attention and accuracy are conceptualized as dissociable interoceptive dimensions. 
<!-- Moreover, the current subjective measures do not correlate well with the objective measures [@murphy2019]. -->

As recent findings report the IAS structure controversially, it becomes evident that further analysis into the structure of the IAS is needed. Additionally, the IAS could be developed further from a structural standpoint to be able to capture interoceptive accuracy and abilities accurately (e.g., Brand, et al., 2023). The present paper is divided into two parts. Firstly, it is trying to leverage existing datasets to do a meta-analysis contrasting the traditional structure analysis approach (CFA/SEM) with new approaches Exploratory Graph Analysis (EGA). Secondly, the present study provides an overview of the correlates of the IAS.

>>>>

![Figure 1. Different ways in which interoception can be measured.](figures/measuring_interoception.png)
<!-- TODO: replace with a code chunk that allows for legend -->

@@

<!-- Convergent validity (correlates)  -->
While the assessment of the validity of an interoception scale can be conceived as theoretically challenging, several traits have been used to assess convergent validity for the the IAS, including expected negative associations with alexithymia [@REF], and positive with neuroticism [@ref]. **anything else?**. 
The IAS has also been compared to other interoception scales, yielding a positive correlation with most facets of the MAIA, with the notable exception of **TODO** [@brand2023], and the **TODO** dimension of the Body Perception Questionnaire [BPQ; @campos2021].
<!-- Moreover, the current subjective measures do not correlate well with the objective measures [@murphy2019]. -->

The current study aims at 1) clarifying the structure of the IAS with a meta-analytic approach that leverages existing data and contrasts the traditional CFA/SEM factor-based analyses with graph-based ones such as EGA. 
2) The second part will provide an overview of the dispositional correlates of the IAS, sketching a pattern of associations that is key to better understand the nature, place and role of interoception questionnaires within a larger context.
